Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-30 paper.qmd
Updated Figure 10

@@

```{r}
#| fig-width: 9
#| fig-height: 2
#| fig-cap: "long edge removal"

trimesh_two_curvy2 + trimesh_two_curvy_removed2 + trimesh_two_curvy_removed1 +
  plot_layout(ncol = 3)
```

>>>>

## To plot the distribution of distances

# Define bin width and starting point
bin_width <- hb_obj_two_curvy2$a1
start_point <- bin_width/2

# Create bins and calculate the mean value for each bin range
bins <- seq(start_point, max(distance_two_curvy$distance) + bin_width, 
            by = bin_width)
bin_labels <- bins[-length(bins)] + bin_width / 2  # mean of each bin range

distance_two_curvy_dist <- distance_two_curvy |> 
  mutate(bin = cut(distance, breaks = bins, include.lowest = TRUE, labels = bin_labels)) |>
  dplyr::filter(distance > 0.1) ## To remove a1 distances, since always small

distance_hist <- ggplot(
  distance_two_curvy_dist, aes(x = distance)) +
    geom_histogram(
      aes(y = after_stat(count) / sum(after_stat(count))), 
      binwidth = bin_width) +
  scale_x_continuous(breaks = bin_labels, 
                     labels = c(
                       expression(a[1]),
                       expression(2*a[1]),
                       expression(3*a[1]),
                       expression(4*a[1]),
                       expression(5*a[1]),
                       expression(6*a[1]),
                       expression(7*a[1]),
                       expression(8*a[1])
                     )) +
  geom_vline(xintercept = start_point + 2*bin_width,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  ylab("Proportion of the number of edges") +
  xlab(expression(d^{(2)})) +
  #ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        panel.grid.major.x = element_blank(),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

```{r}
#| fig-cap: "Wireframes with Delaunay triangulation, and two choices of edge removal in \\gD{} and \\pD{}. "

free(distance_hist) + wrap_plots(trimesh_two_curvy2, trimesh_two_curvy_removed2, trimesh_two_curvy_removed1, ncol = 2) 
```
